Computer Science House Constitution

### 2019-11-24 constitution.tex

\asubsubsection{Housing Priority System}
The Housing Priority System is a means for determining the priority a House member has in a Housing issue such as Single Room Assignment or the Assignment of Available Housing.
The member with top priority is the member with on-floor status and the most Housing Priority Points.
Housing points are accumulated during the Housing Evaluation described in \ref{Housing Evaluation}.
\\* \\*
In the event of a tie, the members will be approached simultaneously and if they are unable to decide fairly between themselves, the assignment of priority will be made by random selection of the tied members.
\asubsubsubsection{Single Room Assignments}
When a single room on the House becomes available it is offered to the member who carries the highest Housing Priority as defined in By-Law V, Section H.
If that House member declines the option, it will be offered to the member with the next highest Housing Priority.
This process continues until a member selects to move into the single room.
Once in a single room, a House member retains the assignment until voluntarily giving it up.
It should be noted that members selecting this option must agree to any additional charges applied by the Department of Residence Life for residing in a single room.
\asubsubsubsection{Double Rooms as Single rooms}
During the third week of each semester, if there is no waiting list for residency on the House, any vacant rooms will be offered to House members as single rooms assignments according to the method as described in \ref{Single Room Assignments}.
It should be noted that this does not mean members will be relocated into empty spaces so that the member with top priority is offered the single.
This only applies if there is a totally vacant room.

@@

\asection{Resignations}
An Executive Board Member may resign their position by submitting in writing the reason for resignation to the House Chairperson.
The resignation will be read at the following House Meeting and become effective at that time.
The office will become vacant and the selection process for a new member as described in section \ref{Appointment of an Interim Director} will begin at that time.

Following a resignation, an election must be held for the position vacated within two weeks from when the resignation took place.
To postpone such an election, the Chairman may chair an Immediate Simple Majority Vote \ref{Immediate Vote} \ref{Simple Majority} during a House Meeting prior to the election to delay the election by a specified amount of time.
\asection{Appointment of an Interim Director}
The duties and responsibilities of a vacated office are assumed by the Chairperson or by an Active member that is appointed at the Chairperson's discretion until the new member takes office.
The vote of a vacated Executive Board position shall be cast as an abstention in all Executive Board matters where this vote is required to be cast.

>>>>

\asubsubsection{Housing Priority System}
The Housing Priority System is a means for determining the priority a House member has in a Housing issue such as Single Room Assignment or the Assignment of Available Housing.
The member with top priority is the member with on-floor status and the most Housing Priority Points.
Housing Priority Points are accumulated once per Operating Session at the conclusion of the Membership Evaluation. Each Active Member with On-Floor Status who passes the Membership Evaluation is granted two (2) Housing Priority Points.
\\* \\*
In the event of a tie, the members will be approached simultaneously and if they are unable to decide fairly between themselves, the assignment of priority will be made by random selection of the tied members.
\asubsubsubsection{Single Room Assignments}
When a single room on the House becomes available it is offered to the member who carries the highest Housing Priority as defined in \ref{Housing Priority System}.
In the event of a tie, the members will be approached simultaneously and if they are unable to decide fairly between themselves, the assignment of priority will be made by random selection of the tied members.
If that House member declines the option, it will be offered to the member with the next highest Housing Priority.
This process continues until a member selects to move into the single room.
Once in a single room, a House member retains the assignment until voluntarily giving it up.
It should be noted that members selecting this option must agree to any additional charges applied by the Department of Residence Life for residing in a single room.
\asubsubsubsection{Double Rooms as Single rooms}
During the third week of each semester, if there is no waiting list for residency on the House, any vacant rooms will be offered to House members as single rooms assignments according to the method as described in \ref{Single Room Assignments}.
It should be noted that this does not mean members will be relocated into empty spaces so that the member with top priority is offered the single.
This only applies if there is a totally vacant room.

@@

\asection{Resignations}
An Executive Board Member may resign their position by submitting in writing the reason for resignation to the House Chairperson.
The resignation will be read at the following House Meeting and become effective at that time.
The office will become vacant and the selection process for a new member as described in section \ref{Appointment of an Interim Director} will begin at that time.
Following a resignation, an election must be held for the position vacated within two weeks from when the resignation took place.
To postpone such an election, the Chairman may chair an Immediate Simple Majority Vote \ref{Immediate Vote} \ref{Simple Majority} during a House Meeting prior to the election to delay the election by a specified amount of time.

\asection{Appointment of an Interim Director}
The duties and responsibilities of a vacated office are assumed by the Chairperson or by an Active member that is appointed at the Chairperson's discretion until the new member takes office.
The vote of a vacated Executive Board position shall be cast as an abstention in all Executive Board matters where this vote is required to be cast.
